|

### 2022-12-20 paper_comparison/paper_comparison/paper_comparison.Rmd
title change
title tweak
handle non-normality

Compared to non-linearity and heteroskedasticity, non-normality is usually harder to detect from a residual plot since scatter plot do not readily reveal the marginal distribution. A favourable graphical summary for this task is the quantile-quantile plot. For a consistent comparison, the residual plot of this departure is still presented in plot D of Figure \ref{fig:residual-plot-common-departures}. But since the scatter plot is not optimal for this task, non-normality will not be the focus of this paper. Besides, it is important to note that not all regression models assume normality for the error term, but a certain amount do including the classical normal linear regression model. In the case that the normality assumption is violated, it is expected to observe data points do not center around the horizontal axis and there is an uneven distribution of the number points at both below and above the horizontal axis. For example, given a skewed error distribution, fewer data points and more outliers are on one side of the horizontal axis as shown in plot D of Figure \ref{fig:residual-plot-common-departures}.

@@

@vanderplas2021statistical suggest that $\alpha$ can be estimated using MLE with Equation \ref{eq:c-interesting-expectation}. But for precise estimate of $\alpha$, additional responses to Rorschach lineups, which is a type of lineup consists of only null plots, are required.

@@

Two types of departures, namely non-linearity and heteroskedasticity, were considered with the corresponding data generating process being designed for experiment I and II. As mentioned earlier, residual plot is not suitable for revealing non-normality, thus it was not considered in our experiments.

@@

@@

As mentioned in Section \ref{calculating-p-values}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using Rorschach lineups. Hence, 36 lineups consist of only null plots with all combinations of $n$ and $X_{raw}$ and three replications are designed to be included in experiment III. Note that we generated the lineups using the same simulation mechanism discussed in Section \ref{sampling-from-the-null-distribution} rather than from a null model. We overlooked this detail until the data had been collected. Thus, we used another valid method suggested in vanderplas2021statistical which was designed for typical lineups to estimate $\alpha$ correctly. However, by not using Rorschach lineups, we did lose some accuracy in the estimation. We recommend future studies to generate Rorschach lineups strictly following the definition given by buja_statistical_2009.

@@

@@

For the non-linearity model, the power of all four tests increases as the effect gets larger. The power curve of F-test climbs aggressively from 25% to around 90% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect and remain lower than 25% throughout the period, showing that F-test is way more sensitive to the type of model defects that being considered. Meanwhile, no noticeable visual features can be spotted from the example residuals plots.

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.3, col = "grey") +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = 0, yend = 1), alpha = 0.3, col = "grey") +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

@@

@@

@@

## Lineup selection

```{r cache = TRUE}
vi_survey_with_plot <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  left_join(map_df(1:length(vi_lineup), 
    ~vi_lineup[[.x]]$data %>% 
      group_by(k) %>% 
      summarise(plot_p_value = first(p_value)) %>%
      arrange(k) %>%
      mutate(unique_lineup_id = names(vi_lineup)[.x]) %>%
      mutate(plot_p_value_rank = rank(plot_p_value, ties.method = "min"))) %>%
  pivot_wider(values_from = c(plot_p_value, plot_p_value_rank), names_from = k, names_prefix = "plot_")) %>%
  (function(x) {
      for (i in 1:20)
        x[[paste0("plot_sel_plot_", i)]] <-
          grepl(paste0("_", i, "_"), x$selection) |
          grepl(paste0("^", i, "_"), x$selection) |
          grepl(paste0("_", i, "$"), x$selection) |
          grepl(paste0("^", i, "$"), x$selection)
      x}
    ) %>%
  pivot_longer(plot_p_value_plot_1:plot_sel_plot_20, 
               names_to = c(".value", "plot"), 
               names_pattern = "(.*)_plot_(.+)") 
```

```{r plotsel, fig.cap = "A large amount of subjects select the residuals plot with the lowest p-value. But greater than 50 percent of subjects evenly select other plots."}
vi_survey_with_plot %>%
  mutate(weighted_sel = ifelse(num_selection == 0, 0.05, plot_sel/num_selection)) %>%
  group_by(type) %>%
  mutate(n_eval = n()/20) %>%
  ungroup() %>%
  group_by(type, plot_p_value_rank) %>%
  summarise(weighted_sel = sum(weighted_sel), n_eval = first(n_eval)) %>%
  ggplot() +
  geom_col(aes(plot_p_value_rank, n_eval), fill = "grey", alpha = 0.3) +
  geom_col(aes(plot_p_value_rank, weighted_sel)) +
  facet_wrap(~type) +
  theme_light() +
  ylab("Weighted number of selections") +
  xlab("Plot p-value rank")
```

```{r dataplotsel, fig.cap = "..."}
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  group_by(unique_lineup_id) %>%
  summarise(plot_p_value_rank = first(plot_p_value_rank),
            weighted_detect = sum(weighted_detect),
            n_eval = n()) %>%
  group_by(plot_p_value_rank) %>%
  summarise(weighted_detect = sum(weighted_detect),
            n_eval = sum(n_eval)) %>%
  mutate(plot_p_value_rank_g5 = plot_p_value_rank >= 5) %>%
  group_by(plot_p_value_rank_g5) %>%
  mutate(n_eval = ifelse(plot_p_value_rank_g5, sum(n_eval), n_eval)) %>%
  mutate(weighted_detect = ifelse(plot_p_value_rank_g5, sum(weighted_detect), weighted_detect)) %>%
  ungroup() %>%
  filter(plot_p_value_rank <= 5) %>%
  mutate(plot_p_value_rank = ifelse(plot_p_value_rank == 5, "5+", as.character(plot_p_value_rank))) %>%
  mutate(plot_p_value_rank = factor(plot_p_value_rank, levels = c(as.character(1:5), "5+"))) %>%
  ggplot() +
  geom_col(aes(plot_p_value_rank, n_eval)) +
  geom_col(aes(plot_p_value_rank, weighted_detect, fill = "weighted number of detections")) +
  xlab("Data plot p-value rank") +
  ylab("Number of Lineups") +
  theme(legend.position = "bottom") +
  labs(fill = "")
```

```{r dadtaplotselfacet, fig.cap = "...", fig.height=12, fig.width=16}
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  left_join(vi_survey_with_plot %>%
              filter(!attention_check) %>%
              filter(!null_lineup) %>%
              filter(answer == plot) %>%
              group_by(unique_lineup_id) %>%
              summarise(answer_rank = first(plot_p_value_rank))) %>%
  mutate(weighted_sel = ifelse(num_selection == 0, 0.05, plot_sel/num_selection)) %>%
  group_by(plot_p_value_rank, answer_rank) %>%
  summarise(weighted_sel = sum(weighted_sel)) %>%
  mutate(answer_rank_g5 = answer_rank >= 5) %>%
  group_by(plot_p_value_rank, answer_rank_g5) %>%
  mutate(weighted_sel = ifelse(answer_rank_g5, sum(weighted_sel), weighted_sel)) %>%
  ungroup() %>%
  filter(answer_rank <= 5) %>%
  mutate(answer_rank = ifelse(answer_rank == 5, "5+", as.character(answer_rank))) %>%
  mutate(answer_rank = factor(answer_rank, levels = c(as.character(1:5), "5+"))) %>%
  ggplot() +
  geom_col(aes(factor(plot_p_value_rank), weighted_sel)) +
  geom_vline(data = data.frame(answer_rank = c("1", "2", "3", "4"), x = 1:4),
             aes(xintercept = x),
             col = "red") +
  facet_wrap(~answer_rank, scales = "free_y") +
  xlab("Plot p-value rank") +
  ylab("Weighted number of selections")
```

```{r eval = FALSE}
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  group_by(unique_lineup_id) %>%
  summarise(plot_p_value_rank = first(plot_p_value_rank),
            weighted_detect = sum(weighted_detect),
            n_eval = n(),
            reject = first(conventional_p_value < 0.05)) %>%
  group_by(plot_p_value_rank, reject) %>%
  summarise(weighted_detect = sum(weighted_detect),
            n_eval = sum(n_eval)) %>%
  ggplot() +
  geom_col(aes(factor(plot_p_value_rank), n_eval)) +
  geom_col(aes(factor(plot_p_value_rank), weighted_detect, fill = "weighted number of detections")) +
  xlab("Data plot p-value rank") +
  ylab("Number of Lineups") +
  theme(legend.position = "bottom") +
  labs(fill = "") +
  facet_wrap(~reject)
```

```{r eval = FALSE}
# data plot not always has the lowest conventional p-value
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  ggplot() +
  geom_bar(aes(factor(plot_p_value_rank)))

# according to the rank of the data plot p-value, how many people select it 
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(plot_sel) %>%
  left_join(vi_survey_with_plot %>%
              filter(!attention_check) %>%
              filter(!null_lineup) %>%
              filter(answer == plot) %>%
              group_by(unique_lineup_id) %>%
              summarise(answer_rank = first(plot_p_value_rank))) %>%
  ggplot() +
  geom_bar(aes(factor(plot_p_value_rank))) +
  geom_vline(data = data.frame(answer_rank = 1:20, x = 1:20),
             aes(xintercept = x),
             col = "red") +
  facet_wrap(~answer_rank, scales = "free_y")

# For different rank, percentage of subject select it
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  group_by(unique_lineup_id, set) %>%
  summarise(plot_p_value_rank = first(plot_p_value_rank),
            detect = first(detect),
            type = first(type)) %>%
  ggplot() +
  geom_bar(aes(factor(plot_p_value_rank), fill = detect), position = "fill") +
  geom_hline(yintercept = 0.05) +
  xlab("Data plot p-value rank") +
  ylab("Propotion of subject detecting the data plot")

vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  group_by(unique_lineup_id, set) %>%
  summarise(plot_p_value_rank = first(plot_p_value_rank),
            prop_detect = first(prop_detect)) %>%
  ggplot() +
  geom_boxplot(aes(factor(plot_p_value_rank), prop_detect))

# vi_survey_with_plot %>%
#   filter(!attention_check) %>%
#   filter(!null_lineup) %>%
#   filter(answer == plot) %>%
#   group_by(unique_lineup_id, set) %>%
#   summarise(plot_p_value_rank = first(plot_p_value_rank),
#             conv_detect = first(conventional_p_value < 0.05)) %>%
#   ggplot() +
#   geom_bar(aes(factor(plot_p_value_rank), fill = conv_detect), position = "fill") +
#   xlab("Data plot p-value rank") +
#   ylab("Propotion of subject detecting the data plot")
```

# invesgating interesting lineups

@@

>>>>

Compared to non-linearity and heteroskedasticity, non-normality is usually harder to detect from a residual plot since scatter plot do not readily reveal the marginal distribution. A favourable graphical summary for this task is the quantile-quantile plot. For a consistent comparison, the residual plot of this departure is still presented in plot D of Figure \ref{fig:residual-plot-common-departures}. However, since the scatter plot is not suitable for this task, non-normality will not be the focus of this paper. Besides, it is important to note that not all regression models assume normality for the error term, but a certain amount do including the classical normal linear regression model. In the case that the normality assumption is violated, it is expected to observe data points do not center around the horizontal axis and there is an uneven distribution of the number points at both below and above the horizontal axis. For example, given a skewed error distribution, fewer data points and more outliers are on one side of the horizontal axis as shown in plot D of Figure \ref{fig:residual-plot-common-departures}.

@@

@vanderplas2021statistical suggest that $\alpha$ can be estimated using MLE with Equation \ref{eq:c-interesting-expectation}. But for precise estimate of $\alpha$, additional responses to Rorschach lineups, which is a type of lineup that consists of

plots constructed from the same null data generating mechnisam.

@@

Two types of departures, namely non-linearity and heteroskedasticity, were considered with the corresponding data generating process being designed for experiment I and II.

@@

(handbook of mathathetical function, https://aapt.scitation.org/doi/10.1119/1.15378, cite the package)

(hermite poly is created by ... in 18..,)

@@

As mentioned in Section \ref{calculating-p-values}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using Rorschach lineups. Hence, 36 lineups consist of only null plots with all combinations of $n$ and $X_{raw}$ and three replications are designed to be included in experiment III. Note that we generated the lineups using the same simulation mechanism discussed in Section \ref{sampling-from-the-null-distribution} rather than from a null model.

(it has zero effect size, an alternative to Rorschach lineups)

(Appendix: vary the alpha a little bit and see how the curves change, sensitivity analysis)

Thus, we used another valid method suggested in vanderplas2021statistical which was designed for typical lineups to estimate $\alpha$ correctly. However, by not using Rorschach lineups, we did lose some accuracy in the estimation. (questionable)

We recommend future studies to generate Rorschach lineups strictly following the definition given by buja_statistical_2009.

@@

(discuss choice of tests, mention pkg `lmtest`, `skedastic`)

@@

For the non-linearity model, the power of all four tests increases as the effect gets larger. The power curve of RESET test climbs aggressively from 13% to around 70% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect and remain lower than 25% throughout the period, showing that F-test is way more sensitive to the type of model defects that being considered. Meanwhile, no noticeable visual features can be spotted from the example residuals plots.

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                filter(x_dist == "uniform") %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = -Inf, yend = Inf), alpha = 0.3, col = "grey") +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

@@

```{r}
p <- vi_survey %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject_dirichlet = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(heter_conv_sim, log_effect_size = log(effect_size)) %>%
                filter(x_dist == "uniform") %>%
                select(-(RESET5_p_value:RESET10_p_value)) %>%
                select(-RESET3_p_value, -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject_dirichlet) %>% 
               summarise(num_response = n()),
             aes(log_effect_size, reject_dirichlet, size = factor(num_response)), alpha = 0.3)  +
  geom_segment(data = data.frame(xi = es), aes(x = xi, xend = xi, y = -Inf, yend = Inf), alpha = 0.3, col = "grey") +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "", size = "#lineups")

@@

(top: curves)
(middle: dots)
(bottom: vertical lines/grid lines)

@@

(style similar to mosaic plot)

(lineups detected by visual test but not by conventional tests)

@@

<!-- ## Lineup selection -->

<!-- ```{r cache = TRUE} -->
<!-- vi_survey_with_plot <- vi_survey %>% -->
<!--   filter(!attention_check) %>% -->
<!--   filter(!null_lineup) %>% -->
<!--   left_join(map_df(1:length(vi_lineup),  -->
<!--     ~vi_lineup[[.x]]$data %>%  -->
<!--       group_by(k) %>%  -->
<!--       summarise(plot_p_value = first(p_value)) %>% -->
<!--       arrange(k) %>% -->
<!--       mutate(unique_lineup_id = names(vi_lineup)[.x]) %>% -->
<!--       mutate(plot_p_value_rank = rank(plot_p_value, ties.method = "min"))) %>% -->
<!--   pivot_wider(values_from = c(plot_p_value, plot_p_value_rank), names_from = k, names_prefix = "plot_")) %>% -->
<!--   (function(x) { -->
<!--       for (i in 1:20) -->
<!--         x[[paste0("plot_sel_plot_", i)]] <- -->
<!--           grepl(paste0("_", i, "_"), x$selection) | -->
<!--           grepl(paste0("^", i, "_"), x$selection) | -->
<!--           grepl(paste0("_", i, "$"), x$selection) | -->
<!--           grepl(paste0("^", i, "$"), x$selection) -->
<!--       x} -->
<!--     ) %>% -->
<!--   pivot_longer(plot_p_value_plot_1:plot_sel_plot_20,  -->
<!--                names_to = c(".value", "plot"),  -->
<!--                names_pattern = "(.*)_plot_(.+)")  -->
<!-- ``` -->

<!-- ```{r plotsel, fig.cap = "A large amount of subjects select the residuals plot with the lowest p-value. But greater than 50 percent of subjects evenly select other plots."} -->
<!-- vi_survey_with_plot %>% -->
<!--   mutate(weighted_sel = ifelse(num_selection == 0, 0.05, plot_sel/num_selection)) %>% -->
<!--   group_by(type) %>% -->
<!--   mutate(n_eval = n()/20) %>% -->
<!--   ungroup() %>% -->
<!--   group_by(type, plot_p_value_rank) %>% -->
<!--   summarise(weighted_sel = sum(weighted_sel), n_eval = first(n_eval)) %>% -->
<!--   ggplot() + -->
<!--   geom_col(aes(plot_p_value_rank, n_eval), fill = "grey", alpha = 0.3) + -->
<!--   geom_col(aes(plot_p_value_rank, weighted_sel)) + -->
<!--   facet_wrap(~type) + -->
<!--   theme_light() + -->
<!--   ylab("Weighted number of selections") + -->
<!--   xlab("Plot p-value rank") -->
<!-- ``` -->

<!-- ```{r dataplotsel, fig.cap = "..."} -->
<!-- vi_survey_with_plot %>% -->
<!--   filter(!attention_check) %>% -->
<!--   filter(!null_lineup) %>% -->
<!--   filter(answer == plot) %>% -->
<!--   group_by(unique_lineup_id) %>% -->
<!--   summarise(plot_p_value_rank = first(plot_p_value_rank), -->
<!--             weighted_detect = sum(weighted_detect), -->
<!--             n_eval = n()) %>% -->
<!--   group_by(plot_p_value_rank) %>% -->
<!--   summarise(weighted_detect = sum(weighted_detect), -->
<!--             n_eval = sum(n_eval)) %>% -->
<!--   mutate(plot_p_value_rank_g5 = plot_p_value_rank >= 5) %>% -->
<!--   group_by(plot_p_value_rank_g5) %>% -->
<!--   mutate(n_eval = ifelse(plot_p_value_rank_g5, sum(n_eval), n_eval)) %>% -->
<!--   mutate(weighted_detect = ifelse(plot_p_value_rank_g5, sum(weighted_detect), weighted_detect)) %>% -->
<!--   ungroup() %>% -->
<!--   filter(plot_p_value_rank <= 5) %>% -->
<!--   mutate(plot_p_value_rank = ifelse(plot_p_value_rank == 5, "5+", as.character(plot_p_value_rank))) %>% -->
<!--   mutate(plot_p_value_rank = factor(plot_p_value_rank, levels = c(as.character(1:5), "5+"))) %>% -->
<!--   ggplot() + -->
<!--   geom_col(aes(plot_p_value_rank, n_eval)) + -->
<!--   geom_col(aes(plot_p_value_rank, weighted_detect, fill = "weighted number of detections")) + -->
<!--   xlab("Data plot p-value rank") + -->
<!--   ylab("Number of Lineups") + -->
<!--   theme(legend.position = "bottom") + -->
<!--   labs(fill = "") -->
<!-- ``` -->

<!-- ```{r dadtaplotselfacet, fig.cap = "...", fig.height=12, fig.width=16} -->
<!-- vi_survey_with_plot %>% -->
<!--   filter(!attention_check) %>% -->
<!--   filter(!null_lineup) %>% -->
<!--   filter(type == "polynomial") %>% -->
<!--   left_join(vi_survey_with_plot %>% -->
<!--               filter(!attention_check) %>% -->
<!--               filter(!null_lineup) %>% -->
<!--               filter(answer == plot) %>% -->
<!--               group_by(unique_lineup_id) %>% -->
<!--               summarise(answer_rank = first(plot_p_value_rank))) %>% -->
<!--   mutate(weighted_sel = ifelse(num_selection == 0, 0.05, plot_sel/num_selection)) %>% -->
<!--   group_by(plot_p_value_rank, answer_rank) %>% -->
<!--   summarise(weighted_sel = sum(weighted_sel)) %>% -->
<!--   mutate(answer_rank_g5 = answer_rank >= 5) %>% -->
<!--   group_by(plot_p_value_rank, answer_rank_g5) %>% -->
<!--   mutate(weighted_sel = ifelse(answer_rank_g5, sum(weighted_sel), weighted_sel)) %>% -->
<!--   ungroup() %>% -->
<!--   filter(answer_rank <= 5) %>% -->
<!--   mutate(answer_rank = ifelse(answer_rank == 5, "5+", as.character(answer_rank))) %>% -->
<!--   mutate(answer_rank = factor(answer_rank, levels = c(as.character(1:5), "5+"))) %>% -->
<!--   ggplot() + -->
<!--   geom_col(aes(factor(plot_p_value_rank), weighted_sel)) + -->
<!--   geom_vline(data = data.frame(answer_rank = c("1", "2", "3", "4"), x = 1:4), -->
<!--              aes(xintercept = x), -->
<!--              col = "red") + -->
<!--   facet_wrap(~answer_rank, scales = "free_y") + -->
<!--   xlab("Plot p-value rank") + -->
<!--   ylab("Weighted number of selections") -->
<!-- ``` -->

<!-- ```{r eval = FALSE} -->
<!-- vi_survey_with_plot %>% -->
<!--   filter(!attention_check) %>% -->
<!--   filter(!null_lineup) %>% -->
<!--   filter(answer == plot) %>% -->
<!--   group_by(unique_lineup_id) %>% -->
<!--   summarise(plot_p_value_rank = first(plot_p_value_rank), -->
<!--             weighted_detect = sum(weighted_detect), -->
<!--             n_eval = n(), -->
<!--             reject = first(conventional_p_value < 0.05)) %>% -->
<!--   group_by(plot_p_value_rank, reject) %>% -->
<!--   summarise(weighted_detect = sum(weighted_detect), -->
<!--             n_eval = sum(n_eval)) %>% -->
<!--   ggplot() + -->
<!--   geom_col(aes(factor(plot_p_value_rank), n_eval)) + -->
<!--   geom_col(aes(factor(plot_p_value_rank), weighted_detect, fill = "weighted number of detections")) + -->
<!--   xlab("Data plot p-value rank") + -->
<!--   ylab("Number of Lineups") + -->
<!--   theme(legend.position = "bottom") + -->
<!--   labs(fill = "") + -->
<!--   facet_wrap(~reject) -->
<!-- ``` -->

<!-- ```{r eval = FALSE} -->
<!-- # data plot not always has the lowest conventional p-value -->
<!-- vi_survey_with_plot %>% -->
<!--   filter(!attention_check) %>% -->
<!--   filter(!null_lineup) %>% -->
<!--   filter(answer == plot) %>% -->
<!--   ggplot() + -->
<!--   geom_bar(aes(factor(plot_p_value_rank))) -->

<!-- # according to the rank of the data plot p-value, how many people select it  -->
<!-- vi_survey_with_plot %>% -->
<!--   filter(!attention_check) %>% -->
<!--   filter(!null_lineup) %>% -->
<!--   filter(plot_sel) %>% -->
<!--   left_join(vi_survey_with_plot %>% -->
<!--               filter(!attention_check) %>% -->
<!--               filter(!null_lineup) %>% -->
<!--               filter(answer == plot) %>% -->
<!--               group_by(unique_lineup_id) %>% -->
<!--               summarise(answer_rank = first(plot_p_value_rank))) %>% -->
<!--   ggplot() + -->
<!--   geom_bar(aes(factor(plot_p_value_rank))) + -->
<!--   geom_vline(data = data.frame(answer_rank = 1:20, x = 1:20), -->
<!--              aes(xintercept = x), -->
<!--              col = "red") + -->
<!--   facet_wrap(~answer_rank, scales = "free_y") -->

<!-- # For different rank, percentage of subject select it -->
<!-- vi_survey_with_plot %>% -->
<!--   filter(!attention_check) %>% -->
<!--   filter(!null_lineup) %>% -->
<!--   filter(answer == plot) %>% -->
<!--   group_by(unique_lineup_id, set) %>% -->
<!--   summarise(plot_p_value_rank = first(plot_p_value_rank), -->
<!--             detect = first(detect), -->
<!--             type = first(type)) %>% -->
<!--   ggplot() + -->
<!--   geom_bar(aes(factor(plot_p_value_rank), fill = detect), position = "fill") + -->
<!--   geom_hline(yintercept = 0.05) + -->
<!--   xlab("Data plot p-value rank") + -->
<!--   ylab("Propotion of subject detecting the data plot") -->

<!-- vi_survey_with_plot %>% -->
<!--   filter(!attention_check) %>% -->
<!--   filter(!null_lineup) %>% -->
<!--   filter(answer == plot) %>% -->
<!--   group_by(unique_lineup_id, set) %>% -->
<!--   summarise(plot_p_value_rank = first(plot_p_value_rank), -->
<!--             prop_detect = first(prop_detect)) %>% -->
<!--   ggplot() + -->
<!--   geom_boxplot(aes(factor(plot_p_value_rank), prop_detect)) -->

<!-- # vi_survey_with_plot %>% -->
<!-- #   filter(!attention_check) %>% -->
<!-- #   filter(!null_lineup) %>% -->
<!-- #   filter(answer == plot) %>% -->
<!-- #   group_by(unique_lineup_id, set) %>% -->
<!-- #   summarise(plot_p_value_rank = first(plot_p_value_rank), -->
<!-- #             conv_detect = first(conventional_p_value < 0.05)) %>% -->
<!-- #   ggplot() + -->
<!-- #   geom_bar(aes(factor(plot_p_value_rank), fill = conv_detect), position = "fill") + -->
<!-- #   xlab("Data plot p-value rank") + -->
<!-- #   ylab("Propotion of subject detecting the data plot") -->
<!-- ``` -->

@@

### A collection interesting lineups (unusual results)

why unusual? what is the possible explanations?

# targe journal

JRSSB: Journal of the Royal Statistical Society Series B (Statistical Methodology)
Deadline: Jan 1, Apr 1

Reading: style of writing, author guideline (https://rss.onlinelibrary.wiley.com/hub/journal/14679868/author-guidelines)

JCGS
JDSS
